---
title: "GEOG_5229_Final"
author: "Quazi Samaul Islam, Syan Raval, and Tirth Patel"
date: "2024-11-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = 'false'}
library(dplyr)
library(ggplot2)
library(stringr)
library(sf)
library(ggmap)
library(tmap)
library(tigris)
library(spatstat)
library(spdep)
library(spatialreg)
library(purrr)
library(lubridate)
library(ggspatial)
```

# Preparing the data

```{r, results = 'hide'}
# Loading LA County Boundary
la_county <- counties(state = "CA", cb = TRUE) %>%
  filter(NAME == "Los Angeles")

common_crs <- st_crs(la_county)
```

```{r}
# Loading California counties for smaller scale
counties <- counties(state = 'CA', cb = TRUE)
counties <- st_transform(counties, common_crs)
```

```{r}
# Loading and cleaning fire stations data set for relevant study area
fire_stations <- read.csv("~/raval27/GEOG 5229/Final Project/Fire_Stations.csv")

fire_stations_lac <- fire_stations %>%
  filter(org_name %in% c("Los Angeles County Fire Department"),
         state == "CA") %>%  # We only want to filter based on org_name and state
  select(OBJECTID, org_name, city, state, latitude, longitude, POINT_X, POINT_Y)

fire_stations_lac <- st_as_sf(fire_stations_lac, coords = c("longitude", "latitude"), crs = 4326)
fire_stations_lac <- st_transform(fire_stations_lac, common_crs)
fire_stations_lac <- st_set_geometry(fire_stations_lac, "geometry")
```

```{r}
# Loading and cleaning historical wildfire perimeters data set for relevant study area

wildfires <- st_read("~/raval27/GEOG 5229/Final Project/California_Fire_Perimeters_(all)/California_Fire_Perimeters_(all).shp")

wildfires <- st_transform(wildfires, common_crs)

wildfires_lac <- wildfires %>%
  filter(UNIT_ID %in% c("LAC", "Los Angeles County"), YEAR_ == "2022") %>%
  mutate(ALARM_DATE = as.Date(ALARM_DATE, format = "%Y/%m/%d"))
```

```{r}
# # Combines weekly drought data into single drought shapefile and adds time column with weeks being last 8 characters of each shapefile name
# 
# shapefiles <- list.files(path = "~/raval27/GEOG 5229/Final Project/Drought Data/", pattern = "\\.shp$", full.names = TRUE)
# 
# # Function to read, add time column, and clip shapefile to LA County
# process_shapefile <- function(shapefile_path) {
#   # Extract date from filename (last 8 characters)
#   date_str <- substr(basename(shapefile_path), nchar(basename(shapefile_path)) - 11, nchar(basename(shapefile_path)) - 4)
#   
#   # Read shapefile
#   shape <- st_read(shapefile_path)
#   
#   # Add time column
#   shape$time <- date_str
#   
#   shape_transformed <- st_transform(shape, st_crs(la_county))
#   shape_fixed <- st_make_valid(shape_transformed)
#   
#   # Clip to LA County (assuming la_county is defined)
#   clipped <- st_intersection(shape_fixed, la_county)
#   
#   return(clipped)
# }
# 
# # Process all shapefiles
# processed_shapes <- map(shapefiles, process_shapefile)
# 
# # Combine all processed shapes into a single data frame
# drought_data <- bind_rows(processed_shapes)
# 
# st_write(drought_data, "~/raval27/GEOG 5229/Final Project/merged_drought_la.shp", append=FALSE)

drought_data_lac <- st_read("~/raval27/GEOG 5229/Final Project/merged_drought_la.shp")
drought_data_lac <- st_transform(drought_data_lac, common_crs)

drought_data_lac <- drought_data_lac %>%
  mutate(time = as.Date(time, format = "%Y%m%d"))
```

## Question 1: Can we identify high-risk wildfire zones in Los Angeles County based on historical fire perimeters, distance from fire stations, and drought severity?

```{r}
print(head(fire_stations_lac))
print(nrow(fire_stations_lac))
```

```{r attempt #1}
ggplot(data = wildfires_lac) +
  geom_sf(aes(fill = ALARM_DATE), size = 2) + scale_fill_viridis_c(name = "Alarm Date") + theme_minimal() +
  labs(
    title = "Wildfires in Los Angeles County",
    subtitle = "Filtered by Specific Alarm Dates",
    caption = "Source: California Fire Perimeters"
  )
```

```{r attempt #2}
ggplot(data = wildfires_lac) +
  geom_sf(aes(fill = ALARM_DATE), size = 0.5) +
  scale_fill_viridis_c(name = "Alarm Date") +
  coord_sf(
    xlim = c(-118.7, -118.1),  # adjust longitude range
    ylim = c(33.8, 34.3),      # adjust latitude range
    expand = FALSE
  ) +
  theme_minimal() +
  labs(
    title = "Zoomed-in Wildfires in Los Angeles County",
    subtitle = "Filtered by Specific Alarm Dates",
    caption = "Source: California Fire Perimeters"
  )
```

```{r mutating the data with area_km2}
wildfires_lac <- wildfires_lac %>%
  mutate(area_km2 = as.numeric(st_area(geometry) / 1e6)) #using mutate to find the area_km2 for geometry
```

```{r attempt #3 (results seen in visualization)}
ggplot(data = wildfires_lac) +
  geom_sf(aes(fill = area_km2), size = 80) + # visualizing using the area_km2
  scale_fill_viridis_c(name = "Area (km²)") +
  theme_minimal() +
  labs(
    title = "Wildfires in Los Angeles County (2022)",
    subtitle = "Visualizing Wildfire Locations and Sizes",
    caption = "Source: California Fire Perimeters",
    x = "Longitude",
    y = "Latitude"
  )
```

### Analysis of the Wildfire Zones

```{r}
# creating a buffer around wildfire zones
wildfire_buffer <- st_buffer(wildfires_lac, dist = 5000)  # 5 km buffer
wildfire_buffer <- st_transform(wildfire_buffer, common_crs)
```

```{r Visualization}
tm_shape(la_county) +
  tm_borders() + # adding the la county's border to the map
  tm_shape(wildfire_buffer) +
  tm_fill(col = "green", alpha = 1) + # indicates wildfire zones
  
  #overlaying drought data with severity levels represented by a color gradient
  tm_shape(drought_data_lac) +
  tm_fill(col = "DM", palette = c("blue", "yellow", "orange", "red", "purple"), 
          title = "Drought Severity", alpha = 0.1) + # columns showing the drought severity
  
  # plotting the fire stations
  tm_shape(fire_stations_lac) +
  tm_dots(col = "black", size = 0.2) + # using blue dots to represent them
  tm_layout(main.title = "Wildfire Zones in LA County with Drought Severity and Fire Stations",
            main.title.size = 0.6, #Adjusting the title size to fit the whole title
            legend.position = c("left", "bottom")) # legend
```

```{r}
tm_shape(la_county) +
  tm_fill(col = NA) +  # add a transparent fill for LA County
  tm_borders(lwd = 1.5, col = "black") +  # show LA County boundaries clearly
  tm_shape(drought_data_lac) + 
  tm_fill(
    col = "DM", 
    palette = c("blue", "yellow", "orange", "green", "purple"), 
    title = "Drought Severity", 
    alpha = 0.5  # make drought polygons semi-transparent
  ) +  
  tm_shape(wildfire_buffer) + 
  tm_fill(
    col = "red", 
    alpha = 0.4, 
    title = "Wildfire Zones"  # ensuring wildfire zones are distinguishable
  ) +  
  tm_shape(fire_stations_lac) +
  tm_dots(
    col = "black", 
    size = 0.2, 
    title = "Fire Stations"
  ) +  
  tm_layout(
    main.title = "Wildfire Zones in LA County with Drought Severity and Fire Stations", 
    legend.position = c("left", "bottom"), 
    legend.bg.color = "white",  # this adds a background to the legend for readability
    legend.bg.alpha = 0.7  # slight transparency for the legend background
  )
```

### Spatial Join: Drought Severity and Wildfires
```{r}
wildfire_drought_intersection <- st_intersection(wildfires_lac, drought_data_lac) # for wildfires intersecting with the drought

head(wildfire_drought_intersection)
```

```{r}
wildfire_drought_severity <- wildfire_drought_intersection %>%
  group_by(FIRE_NAME) %>% # group data bu using wildfire number (FIRE_NUM)
  summarize(drought_severity = max(DM, na.rm = TRUE))

# View the results
head(wildfire_drought_severity)
```

```{r}
wildfire_drought_join <- st_join(wildfires_lac, drought_data_lac, join = st_intersects) #join wildfire and drought data based on spatial intersection

# visualize wildfire zones, drought severity, and fire stations in LA County
tm_shape(la_county) +
  tm_borders() +  # show LA County boundaries
  tm_shape(wildfire_drought_join) + 
  tm_fill(col = "DM", palette = c("blue", "yellow", "orange", "red", "purple"), 
          title = "Drought Severity", alpha = 0.5) +             # drought severity fill
  tm_shape(fire_stations_lac) +
  tm_dots(col = "gray", size = 0.2, alpha = 0.3) +  # add fire stations as blue dots
  tm_layout(main.title = "Wildfire Zones and Drought Severity in LA County",
            main.title.size = 0.6,
            legend.position = c("left", "bottom"))
```

```{r}
wildfire_buffer <- st_buffer(wildfires_lac, dist = 5000)  # 5 km buffer

tm_shape(la_county) +
  tm_borders() +
  tm_shape(wildfire_buffer) +
  tm_fill(col = "red", alpha = 0.4) +  # buffer zones in red
  tm_shape(wildfire_drought_join) +
  tm_fill(col = "DM", palette = c("blue", "yellow", "orange", "red", "purple"), 
          title = "Drought Severity", alpha = 0.5) +
  tm_shape(fire_stations_lac) +
  tm_dots(col = "gray", size = 0.2, alpha = 0.2) +
   tm_layout(main.title = "Wildfire Zones, Drought Severity, and Fire Stations in LA County",
            main.title.size = 0.6,
            legend.position = c("left", "bottom"))
```

### Proximity Analysis: Fire Stations and Wildfires
```{r}
fire_station_buffer <- st_buffer(fire_stations_lac, dist = 10000)  # 10 km buffer

# join fire stations to the wildfire buffer zone to check proximity
fire_station_near_wildfires <- st_join(fire_station_buffer, wildfire_buffer)

# count the number of fire stations within the buffer for each wildfire
fire_station_count_per_wildfire <- fire_station_near_wildfires %>%
  group_by(FIRE_NAME) %>%
  summarize(fire_station_count = n())
```

```{r}
fire_station_count_per_wildfire <- st_make_valid(fire_station_near_wildfires)
```

```{r}
print(fire_station_count_per_wildfire)
```

```{r}
tm_shape(la_county) +
  tm_borders() +
  tm_shape(fire_station_buffer) +
  tm_fill(col = "lightblue", alpha = 0.5, title = "Fire Station Buffer") + # highlight the buffer zones around fire stations
  tm_shape(wildfire_buffer) +
  tm_fill(col = "orange", alpha = 0.5, title = "Wildfire Zones") +  # show wildfire zones with semi-transparent orange fill
  tm_shape(fire_stations_lac) +
  tm_dots(col = "red", size = 0.2, title = "Fire Stations") +  # adjust size for visibility
  tm_layout(main.title = "Proximity of Wildfires to Fire Stations in LA County", 
            main.title.size = 0.7,
            legend.position = c("left", "bottom"))
```

### Identifying High Risk Zones using Spatial Analysis

```{r}

# wildfire_risk_analysis <- st_union(drought_data_lac, fire_station_count_per_wildfire)
# 
# # add a new "risk_score" column to the wildfire_risk_analysis dataset
# wildfire_risk_analysis <- wildfire_risk_analysis %>%
#   mutate(
#     risk_score = case_when(
#       (DM == 5) & (fire_station_count >= 1) ~ "High Risk",      # assigning high risk
#       (DM >= 4) & (fire_station_count >= 1) ~ "Moderate Risk",  #   ''      moderate risk
#       TRUE ~ "Low Risk"                                                   # low risk
#     )
#   )

```

```{r}
# head(wildfire_risk_analysis)
```

```{r}

# # create a frequency table of the "risk_score" variable
# table(wildfire_risk_analysis$risk_score)
# 
# # make sure that risk_score is a factor with the proper levels
# wildfire_risk_analysis$risk_score <- factor(wildfire_risk_analysis$risk_score, # function using th erisk_scores
#                                              levels = c("Low Risk", "Moderate Risk", "High Risk")) # levels of risk
# 
# # checking again
# table(wildfire_risk_analysis$risk_score)

```

```{r}
# '
# tm_shape(la_county) +
#   tm_borders() +
#   tm_shape(wildfire_risk_analysis) +
#   tm_fill(col = "risk_score", palette = c("Low Risk" = "green", "Moderate Risk" = "yellow", "High Risk" = "red")) + # using risk score to assign colors for zones
#   tm_shape(fire_stations_lac) +
#   tm_dots(col = "blue", size = 0.3, title = "Fire Stations") +
#   tm_layout(main.title = "High-Risk Wildfire Zones in LA County (2022)", legend.position = c("left", "bottom"))
# '
```
### Moran test

```{r}
# spatial join for wildfire and drought severity
wildfire_drought_join <- st_join(wildfires_lac, drought_data_lac, join = st_intersects)

# assign risk scores based on drought severity
wildfire_drought_join <- wildfire_drought_join %>%
  mutate(
    risk_score = case_when(
      DM == 5 ~ "High Risk",
      DM >= 3 ~ "Moderate Risk",
      TRUE ~ "Low Risk"
    )
  )

# convert risk score to a factor and assign numeric levels
wildfire_drought_join$risk_score <- factor(
  wildfire_drought_join$risk_score, 
  levels = c("Low Risk", "Moderate Risk", "High Risk")
)
risk_score_numeric <- as.numeric(wildfire_drought_join$risk_score)

# create spatial neighbors and weight matrix
neighbors <- poly2nb(as_Spatial(wildfire_drought_join))  # queen contiguity
weights <- nb2listw(neighbors, style = "W")              # row-standardized weights

#  perform Moran's I test
moran_result <- moran.test(risk_score_numeric, listw = weights)

# display the Moran's I test results
print(moran_result)
```

```{r}
moran_result_value <- moran_result$estimate[1]  # Moran's I statistic

tm_shape(wildfire_drought_join) +
  tm_borders() +
  tm_fill(col = "risk_score", 
          palette = c("Low Risk" = "green", "Moderate Risk" = "yellow", "High Risk" = "red")) +
  tm_layout(main.title = paste("Moran's I =", round(moran_result_value, 3)),
            legend.position = c("left", "bottom"))
```
```{r}
# 
# plot(moran_data$observed, moran_data$lagged,
#      xlab = "Observed Risk Score", ylab = "Lagged Risk Score",
#      main = "Morans I Scatter Plot",
#      col = "blue", pch = 16)
# abline(h = mean(moran_data$lagged), col = "red", lwd = 2)  # red line represents the average lagged value
# 
```

## Question 2: What is the spatial relationship between areas of high drought severity and the frequency of small (<500 acres) wildfires in Los Angeles County?

```{r}
ggplot() +
  geom_sf(data = la_county, fill = "grey", color = "black", size = 0.2) +
  geom_sf(data = drought_data_lac, aes(fill = DM), alpha = 0.6) +
  scale_fill_viridis_c(option = "plasma", name = "Drought Metric") +
  labs(
    title = "Drought Severity in Los Angeles County",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme_minimal()
```

```{r}
# filter wildfire data to include fire under 500 acres.
small_wildfires <- wildfires_lac %>% filter(GIS_ACRES < 500)

# Overlay these wildifre points on the drought map

ggplot() +
  geom_sf(data = la_county, fill = "grey", color = "black", size = 0.2) +
  geom_sf(data = drought_data_lac, aes(fill = DM), alpha = 0.6) +
  geom_sf(data = small_wildfires, aes(color = "Small Wildfires"), size = 1.5, alpha = 0.8) +
  scale_fill_viridis_c(option = "plasma", name = "Drought Metric") +
  scale_color_manual(values = c("Small Wildfires" = "red"), name = "Wildfire Type") +
  labs(
    title = "Small Wildfires and Drought Severity in Los Angeles County",
    x = "Longitude",
    y = "Latitude"
  ) +
  coord_sf(
    xlim = c(-118.9, -117.6),  # Adjust longitude range
    ylim = c(33.7, 34.8)       # Adjust latitude range
  ) +
  theme_minimal()
```

```{r}
# reproject to the same coordiante system 
small_wildfires <- st_transform(small_wildfires, st_crs(drought_data_lac))
# Perform a spatial join to associate each small wildfire with the drought severity level of the region it overlaps
wildfires_drought <- st_join(small_wildfires, drought_data_lac)

# Analyze wildifire frequency by drought level
wildfire_summary <- wildfires_drought %>%
  group_by(DM) %>%
  summarize(frequency = n())
print(wildfire_summary)
```

```{r}
# Conducting a point pattern analysis to project wildifre data to spatial points
# First reproject both small wildfires and la county wgs84 to la county CRS

small_wildfires_projected <- st_transform(small_wildfires, 32611)  # Reproject wildfires
la_county_projected <- st_transform(la_county, 32611)       # Reproject LA County

wildfire_ppp <- as.ppp(
  st_coordinates(small_wildfires_projected),
  W = as.owin(st_bbox(la_county_projected))  # Create observation window from LA County boundary
)

summary(wildfire_ppp)
```

```{r}
# Using k-function to detect clustering
K <- Kest(wildfire_ppp)
plot(K)

quadrat <- quadrat.test(wildfire_ppp, nx = 5, ny = 5)
print(quadrat)
```

```{r}
wildfires_drought <- st_join(small_wildfires, drought_data_lac, join = st_intersects)

# Remove rows with missing values
wildfires_drought <- wildfires_drought[!is.na(wildfires_drought$DM) & !is.na(wildfires_drought$frequency), ]

centroids <- st_centroid(small_wildfires)
coords <- st_coordinates(small_wildfires)
coords_clean <- coords[, 1:2]
# prepare spatial data 

wildfire_data <- data.frame(
  DM = wildfires_drought$DM,
  frequency = wildfires_drought$frequency
)

# Define neighbors within 5 km
nb <- dnearneigh(coords_clean, d1 = 0, d2 = 5000)

# Convert neighbors to spatial weights
listw <- nb2listw(nb, style = "W")
```

```{r}
ggplot() +
  # Base map of Los Angeles County
  geom_sf(data = la_county, fill = "grey", color = "black", size = 0.2) +
  
  # Drought severity map
  geom_sf(data = drought_data_lac, aes(fill = DM), alpha = 0.6) +
  
  # Wildfire locations
  geom_sf(data = small_wildfires, aes(color = "Small Wildfires"), size = 1.5, alpha = 0.8) +
  
  # Adjust scales for drought and wildfire
  scale_fill_viridis_c(option = "viridis", name = "Drought Metric") +
  scale_color_manual(values = c("Small Wildfires" = "red"), name = "Wildfire Type") +
  
  # Add labels and titles
  labs(
    title = "Small Wildfires and Drought Severity in Los Angeles County",
    subtitle = "Visualizing the correlation between drought severity and wildfire distribution",
    x = "Longitude",
    y = "Latitude"
  ) +
  
  # Zoom in for better detail
  coord_sf(xlim = c(-119, -117.5), ylim = c(33.5, 34.8)) +
  
  # Minimalist theme
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, hjust = 0.5),
    legend.position = "right"
  )
```

## Question 3: How does the proximity of wildfires to fire stations in Los Angeles County correlate with drought severity, and how does this relationship change over time during the 2022 fire season?

```{r, message = 'false'}
# Calculate the centroid of each wildfire polygon
wildfires_lac$centroid <- st_centroid(wildfires_lac$geometry)

# Calculate the distance from each wildfire centroid to all fire stations
# Then find the minimum distance for each wildfire (i.e., distance to nearest station)
nearest_station_distances <- st_distance(wildfires_lac$centroid, fire_stations_lac)
wildfires_lac$nearest_station_dist <- apply(nearest_station_distances, 1, min)

# Join wildfire data with drought data, filtering for drought data within 7 days of fire start
# Calculate average drought severity for each fire
wildfires_w_drought <- st_join(wildfires_lac, drought_data_lac, join = st_intersects, left = TRUE) %>%
  filter(time >= ALARM_DATE & time <= ALARM_DATE + 7) %>%
  group_by(FIRE_NAME) %>%
  summarize(avg_drought = mean(DM, na.rm = TRUE))

# Calculate overall correlation between fire station distance and drought severity
overall_correlation <- wildfires_lac %>%
  st_join(wildfires_w_drought, join = st_nearest_feature, left = TRUE) %>%
  filter(!is.na(nearest_station_dist) & !is.na(avg_drought)) %>%
  summarize(
    correlation = if(n() >= 3 && n_distinct(avg_drought) > 1) 
                    cor(nearest_station_dist, avg_drought, 
                        method = "spearman", use = "complete.obs") 
                  else NA,
    sample_size = n()
  )

print(overall_correlation)

# Prepare data for plotting by removing geometry
plot_data <- wildfires_lac %>%
  st_join(wildfires_w_drought, join = st_intersects, left = TRUE) %>%
  filter(!is.na(nearest_station_dist) & !is.na(avg_drought)) %>%
  st_drop_geometry()

map_data <- wildfires_lac %>%
  st_join(wildfires_w_drought, join = st_intersects, left = TRUE) %>%
  filter(!is.na(nearest_station_dist) & !is.na(avg_drought))

# Create a scatter plot of fire station distance vs drought severity
ggplot(plot_data, aes(x = nearest_station_dist, y = avg_drought)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", color = "red") +
  geom_text(
    aes(x = max(nearest_station_dist), y = max(avg_drought), 
        label = paste("ρ =", round(overall_correlation$correlation, 3))),
    hjust = 1, vjust = 1
  ) +
  labs(
    title = paste("Correlation between Fire Station Distance and Drought Severity"),
    subtitle = paste("Spearman correlation:", round(overall_correlation$correlation, 3),
                     "| Sample size:", overall_correlation$sample_size),
    x = "Distance to Nearest Fire Station (meters)",
    y = "Average Drought Severity"
  ) +
  theme_minimal()

# Create a scatter plot with points colored by date
ggplot(plot_data, aes(x = nearest_station_dist, y = avg_drought, fill = ALARM_DATE)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", color = "red") +
  scale_color_gradient(low = "blue", high = "red") +
  geom_text(
    aes(x = max(nearest_station_dist), y = max(avg_drought), 
        label = paste("ρ =", round(overall_correlation$correlation, 3))),
    hjust = 1, vjust = 1
  ) +
  labs(
    title = "Correlation between Fire Station Distance and Drought Severity Over Time",
    subtitle = paste("Spearman correlation:", round(overall_correlation$correlation, 3),
                     "| Sample size:", overall_correlation$sample_size),
    x = "Distance to Nearest Fire Station (meters)",
    y = "Average Drought Severity",
    color = "Date"
  ) +
  theme_minimal()

# Create a scatter plot with points connected chronologically
ggplot(plot_data, aes(x = nearest_station_dist, y = avg_drought, fill = ALARM_DATE)) +
  geom_point(alpha = 0.6) +
  geom_path(alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  scale_color_gradient(low = "blue", high = "red") +
  geom_text(
    aes(x = max(nearest_station_dist), y = max(avg_drought), 
        label = paste("ρ =", round(overall_correlation$correlation, 3))),
    hjust = 1, vjust = 1
  ) +
  labs(
    title = "Correlation between Fire Station Distance and Drought Severity Over Time",
    subtitle = paste("Spearman correlation:", round(overall_correlation$correlation, 3),
                     "| Sample size:", overall_correlation$sample_size),
    x = "Distance to Nearest Fire Station (meters)",
    y = "Average Drought Severity",
    color = "Date"
  ) +
  theme_minimal()

ggplot() +
  geom_sf(data = la_county) +
  geom_sf(data = map_data, aes(fill = avg_drought, color = nearest_station_dist), alpha = 0.7) +
  geom_sf(data = fire_stations_lac, color = "red", size = 1, alpha = 0.4) +
  scale_fill_viridis_c(name = "Drought Severity") +
  scale_size_continuous(name = "Distance to Nearest Fire Station (m)") +
  annotation_scale(location = "bl", width_hint = 0.5) +
  theme_minimal() +
  labs(title = "Wildfires, Fire Stations, and Drought Severity in Los Angeles County",
       subtitle = paste("Spearman correlation:", round(overall_correlation$correlation, 3)))
```



